SIMD\slash SIMT-vectorized Sparse Chemical Kinetic Jacobian\slash Thermo-chemical Source Term Evaluation

### 2018-02-22 paper.tex
done for tonight

In~\cref{F:sparse_jac_scaling}, the parallel scaling efficiency of the sparse shallow-vectorized OpenCL is compared to the sparse OpenMP code.
The plot is a bit difficult to read, as most of the data-points are clustered together however the key takeaway is that the parallel scaling efficiency of the shallow-vectorized OpenCL code is much closer in value to that of the OpenMP code as compared to the source rate evaluations (\cref{F:source_parallel_scaling}).
The \ce{H2}\slash\ce{CO} model has the worst scaling for both codes, ranging from \numrange{0.93}{0.54} and \numrange{0.99}{0.86} for OpenCL and OpenMP respectively on \numrange{2}{16} cores.
As the model size increases, the efficiency of the OpenCL code improves dramatically, reaching \numrange{0.997}{0.84} for the isopentanol model.
It is worth noting that the OpenCL code's scaling is more negatively affected by the switch from a single 12-core CPU (\cref{t:cpus}) to two CPUs (i.e., the 16 core data-point) than the OpenMP code.
In contrast,~\cref{F:dense_jac_scaling} shows scaling for the shallow-vectorized dense Jacobian OpenCL code that is higher than for source-rate evaluation, but not as good as for sparse Jacobian evaluation.

@@

>>>>

In~\cref{F:sparse_jac_scaling}, the parallel scaling efficiency of the sparse shallow-vectorized OpenCL is compared to the sparse OpenMP code.
The plot is a bit difficult to read, as most of the data-points are clustered together however the key takeaway is that the parallel scaling efficiency of the shallow-vectorized OpenCL code is much closer in value to that of the OpenMP code as compared to the source rate evaluations (\cref{F:source_parallel_scaling}).
The \ce{H2}\slash\ce{CO} model has the worst scaling for both codes, ranging from \numrange{0.93}{0.54} and \numrange{0.99}{0.86} for OpenCL and OpenMP respectively on \numrange{2}{16} cores.
As the model size increases, the efficiency of the OpenCL code improves dramatically, reaching \numrange{0.997}{0.84} for the isopentanol model.
It is worth noting that the OpenCL code's scaling is more negatively affected by the switch from a single 12-core CPU (\cref{t:cpus}) to two CPUs (i.e., the 16 core data-point) than the OpenMP code.
In contrast,~\cref{F:dense_jac_scaling} shows scaling for the shallow-vectorized dense Jacobian OpenCL code that is higher than for source-rate evaluation, but not as good as for sparse Jacobian evaluation.
In this case, the USC-Mech II model\todo{note: don't have data for ipentanol yet} has the worst scaling for both codes; ranging from \numrange{0.96}{0.63} and \numrange{0.91}{0.34} for OpenMP and OpenCL respectively.
As in~\cref{S:source_results}, we note that the shallow-vectorized OpenCL code on a single core of the \avx/ machine is roughly as fast than the OpenMP code on four cores of the same; hence, the OpenMP code has more room to improve performance before parallel-overhead and memory-bandwidth issues become a limiting concern.

@@

The GPU performance
